Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2020-09-17 write-up/covid-writeup.tex
Update covid-writeup.tex

\begin{table}[!th]
\begin{tabular}{c | c | r r | r | r r }
& & \multicolumn{2}{c}{Total Tests (\%)} & US & \multicolumn{2}{c}{Positive Test Rate (\%)}\\
\cline{3-4} \cline{6-7}
& & NonRandom & Random & Census & NonRandom & Random \\ \hline
\multirow{2}{*}{Sex} & Female & 58 & 55 & 51 & 21.7 & 1.4 \\
& Male & 42 & 45 & 49 & 24.2 & 2.1 \\ \hline
\multirow{3}{*}{Age} & $<40$ & 40 & 28 & 53 & 29.7 & 1.7 \\
& $40-59$ & 41 & 36 & 25 & 24.9 & 2.1 \\
& $\geq 60$ & 19 & 36 & 22 & 6.7 & 0.9 \\ \hline
\multirow{2}{*}{Race} & White & 23 & 92 & 87 & 19.5 & 1.5 \\
& Nonwhite & 77 & 8 & 13 & 25.0 & 3.4 \\ \hline
Hispanic & Hispanic & - & - & - & 37.6 & 6.9 \\
Origin & Non-Hispanic & - & - & - & 13.0 & 1.3 \\ \hline
\multirow{2}{*}{Fever} & Yes & 17.0 & 43 & - & 31.6 & 1.9 \\
& No & 38 & 57 & -& 10.4 & 0.9 \\ \hline
\multirow{2}{*}{Household} & Yes & 11 & 1 & - & 46.1 & 24.4 \\
& No & 89 & 99 & - & 21.6 & 1.3 \\ \hline
Prior $+$ & Yes & 6 & 1 & - & 39.2 & 24.4 \\
Test & No & 94 & 99 & - & 21.6 & 1.3 \\ \hline
\end{tabular}
\caption{Estimated point prevalence of active infection with SARS-CoV-2 by demographics in Indiana.}
\end{table}

We correct the nonrandom sample to match the Indiana state-wide prevalence

>>>>

\begin{table}[!th]
\begin{tabular}{c | c | r r | r | r r }
& & \multicolumn{2}{c}{Total Tests (\%)} & US & \multicolumn{2}{c}{Positive Test Rate (\%)}\\
\cline{3-4} \cline{6-7}
& & NonRandom & Random & Census & NonRandom & Random \\ \hline
\multirow{2}{*}{Sex} & Female & 58.2 & 55.0 & 51 & 21.7 & 1.4 \\
& Male & 42 & 45.0 & 49 & 24.2 & 2.1 \\ \hline
\multirow{3}{*}{Age} & $<40$ & 40 & 28.0 & 53 & 29.7 & 1.7 \\
& $40-59$ & 41 & 36.0 & 25 & 24.9 & 2.1 \\
& $\geq 60$ & 19 & 36.0 & 22 & 6.7 & 0.9 \\ \hline
\multirow{2}{*}{Race} & White & 23 & 92.0 & 87 & 19.5 & 1.5 \\
& Nonwhite & 77 & 8.0 & 13 & 25.0 & 3.4 \\ \hline
Hispanic & Hispanic & - & 2.0 & - & 37.6 & 6.9 \\
Origin & Non-Hispanic & - & 98.0 & - & 13.0 & 1.3 \\ \hline
\multirow{2}{*}{Fever} & Yes & 17.0 & 1.8 & - & 66.4 & 4.5 \\
& No & 83.0 & 98.2 & - & 15.6 & 1.3 \\ \hline
\multirow{2}{*}{Household} & Yes & 10.8 & 1.4 & - & 46.1 & 24.4 \\
& No & 89.2 & 98.6 & - & 21.6 & 1.3 \\ \hline
Prior $+$ & Yes & 6.1 & 1.6 & - & 39.2 & 24.4 \\
Test & No & 93.9 & 98.6 & - & 21.6 & 1.3 \\ \hline
\end{tabular}
\caption{Estimated point prevalence of active infection with SARS-CoV-2 by demographics in Indiana.}
\end{table}

We correct the nonrandom sample to match the Indiana state-wide prevalence.

$66.4 * 0.17 + 15.6 * 0.83 = XX = 11.7 * c $
